Empirical Option Returns and the risk-free Rate in Crypto Asset Markets

### 2024-02-13 written/paper.tex
added eth plots

- scrape 8h funding rate continuously and use as market-interest rate

- scrape all BTC, ETH transactions from Deribit 
- load data, clean
- center on settlement date for each day (10am UTC)
- for each option, find the pendant via put-call-parity
- calculate the beta of each put, call
- build zero-beta straddles by finding weights such that the sum of weights is zero
- assess empirical, daily returns of the straddle
- build boxplots over levels of moneyness
- KDE --> t-distribution
- perform t-test for population mean of 0

- Formulas for the weights!

Ethereum: 
?!
Todo

@@

Instruments, such as inverse options, futures and perpetual futures, have a Mark Price $M$. The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth (quote: 
Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system. Usually, this is the average of the best bid and best ask price. However, for risk management purposes, there is price bandwidth in place.
). The Deribit Index $D$, which is a Lasperes Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.

@@

@@

\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized.png}
    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized_zoom.png}

@@

\end{minipage}
\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth.png}
    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_zoom.png}
    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}

@@

\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
    \captionof{figure}{Performance - Vanilla - No Fees}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
     \captionof{figure}{Performance - Vanilla - Fees}

\end{minipage}
\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
    \captionof{figure}{Performance - Crash Resistant - No Fees}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
     \captionof{figure}{Performance - Crash Resistant - Fees}

>>>>

@@

Instruments, such as inverse options, futures and perpetual futures, have a Mark Price $M$. The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth (quote: 
Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system. Usually, this is the average of the best bid and best ask price. However, for risk management purposes, there is price bandwidth in place.
). The Deribit Index $D$, which is an equally weighted Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.

@@

Ethereum: 
Amount of Observations outside of allowed IV range:  0.017042133327261764
Amount of Observations outside of allowed Tau range:  0.20172172747210984
Overall Observations: 2283869
Amount of Observations in our set post filtering:  1809762

@@

\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized.png}
    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized_zoom.png}

@@

\end{minipage}
\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth.png}
    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_zoom.png}
    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}

@@

\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
     \captionof{figure}{BTC - Performance - Vanilla - Fees}

\end{minipage}
\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}

\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
     \captionof{figure}{ETH - Performance - Vanilla - Fees}

\end{minipage}
\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
